---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/sol-eng/accesstocare/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sol-eng/accesstocare/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/sol-eng/accesstocare/graph/badge.svg)](https://app.codecov.io/gh/sol-eng/accesstocare)
<!-- badges: end -->

  - [Introduction](#introduction)
  - [Analysis Background](#analysis-background)
  - [Installation](#installation)
  - [Usage](#usage)
    - [Copy a specific example](#copy-a-specific-example)
    - [Force overwrite](#force-overwrite)
  - [Publishing to Posit Connect](#publishing-to-posit-connect)
    - [Git-backed deployment](#git-backed-deployment)

## Introduction

An R package to make it easy to view, copy, interact and publish the data 
products resulting from the Access to Care analysis.  It also contains handy
utility functions, and the data needed to create a consistent set of examples 
across the multiple data product types.

## Analysis Background

This project combines US Census population data with hospital data provided by
Medicare. The Census data is as of 2024, and the hospital Medicare data is as of
2025. The analysis uses individual counties as the unit of measurement. A county
is considered underserved based on a linear model that compares the number of hospitals
to the population.  

## Installation

Install `accesstocare` from GitHub using: 

```{r, eval = FALSE}
pak::pak("sol-eng/accesstocare")
```

## Usage

```{r}
library(accesstocare)
```

The package includes multiple example data products demonstrating different ways to visualize and present the Access to Care analysis. Use `create_content()` to copy these examples to your working directory.


```{r, eval = FALSE}
create_content()
```

This will create a separate subfolder for each example in your current working directory. Currently, there are 14 examples available. You can also specify a target directory:

```{r, eval = FALSE}
create_content(target = "my-examples")
```

### Copy a specific example

If you wish to copy a specific example, specify its name:

```{r, eval = FALSE}
create_content(content = "shiny")
```

Available content options include:

- `"connectwidgets"` - Overview application listing all related content
- `"dash"` - Python Dash dashboard
- `"fastapi"` - REST API using FastAPI and Python
- `"htmlwidgets"` - Interactive county-level plot
- `"plot"` - Static ggplot2 map of entire country
- `"plumber-api"` - REST API with multiple endpoints
- `"presentation"` - Quarto presentation (R)
- `"presentation-python"` - Quarto presentation (Python)
- `"quarto-dashboard-python"` - Quarto dashboard with Python, Polars, and Plotnine
- `"quarto-dashboard-r"` - Quarto dashboard by state
- `"quarto-html-python"` - Quarto HTML document with Python, Polars, Plotnine, and Great Tables
- `"RMarkdown-html"` - HTML report with email template
- `"RMarkdown-pdf"` - PDF report
- `"shiny"` - Shiny application

### Force overwrite

By default, `create_content()` skips folders that already exist. Use `force = TRUE` to overwrite:

```{r, eval = FALSE}
create_content(content = "shiny", force = TRUE)
```

## Publishing to Posit Connect

The examples in this package can be published to Posit Connect using the standard push-button deployment from RStudio IDE. However, if you prefer to use Git-backed deployment, the package provides a helper function to create the necessary deployment files.

### Git-backed deployment

[Git-backed deployment](https://docs.posit.co/connect/user/git-backed/) is a Posit Connect feature that automatically deploys and updates your content directly from a Git repository. Instead of pushing content from your local machine, Connect pulls the latest code from your Git repository whenever you commit changes. This enables seamless CI/CD workflows and ensures your published content always matches what's in version control.

**Note:** Using `create_git_backed()` is only necessary if you want to use Git-backed deployment. If you plan to publish manually using an IDE such as RStudio or Positron, you can skip this step.

To prepare content for Git-backed deployment, use the `create_git_backed()` function:

```{r, eval = FALSE}
# Prepare a single folder
create_git_backed("my-examples/shiny")

# Prepare all subfolders in a directory
# This will detect subfolders with deployable content and create necessary files for each
create_git_backed("my-examples")
```

The function intelligently determines what to do:

- **Single folder with content**: If the folder contains a deployable file (like app.R, .Rmd, .qmd, etc.), it creates the necessary deployment files for that folder.
- **Folder with subfolders**: If the folder doesn't contain deployable content but its subfolders do, it will create the necessary files for all qualifying subfolders. In interactive sessions, it will prompt you before executing.

Once the deployment files are created, commit them to your Git repository along with your content, and configure Posit Connect to deploy from your repository. See the [official Git-backed deployment documentation](https://docs.posit.co/connect/user/git-backed/) for complete setup instructions.


