---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/sol-eng/accesstocare/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sol-eng/accesstocare/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/sol-eng/accesstocare/graph/badge.svg)](https://app.codecov.io/gh/sol-eng/accesstocare)
<!-- badges: end -->

  - [Access to Care](#access-to-care)
  - [Analysis Background](#analysis-background)
  - [Installation](#installation)
  - [Usage](#usage)
    - [Copy a specific example](#copy-a-specific-example)
    - [Copy all examples](#copy-all-examples)
    - [Force overwrite](#force-overwrite)

## Access to Care

An R package to make it easy to view, copy, interact and publish the data 
products resulting from the Access to Care analysis.  It also contains handy
utility functions, and the data needed to create a consistent set of examples 
across the multiple data product types.

## Analysis Background 

This project combines US Census population data with hospital data provided by 
Medicare. The Census data is as of 2024, and the hospital Medicare date is as of
2025. The analysis uses individual counties as the unit of measurement. A county
is considered undeserved based on a linear model.  

## Installation

Install `accesstocare` from GitHub using: 

```{r, eval = FALSE}
pak::pak("sol-eng/accesstocare")
```

## Usage

```{r}
library(accesstocare)
```

The package includes multiple example data products demonstrating different ways to visualize and present the Access to Care analysis. Use `create_content()` to copy these examples to your working directory.

### Copy a specific example

Copy a single example by specifying its name:

```{r, eval = FALSE}
create_content(content = "shiny")
```

Available content options include:

- `"connectwidgets"` - Overview application listing all related content
- `"dash"` - Python Dash dashboard
- `"htmlwidgets"` - Interactive county-level plot
- `"jupyter"` - Jupyter Notebook
- `"plot"` - Static ggplot2 map of entire country
- `"plumber-api"` - REST API with multiple endpoints
- `"presentation"` - Quarto presentation
- `"quarto-dashboard-r"` - Quarto dashboard by state
- `"RMarkdown-html"` - HTML report with email template
- `"RMarkdown-pdf"` - PDF report
- `"shiny"` - Shiny application

You can also specify a target directory:

```{r, eval = FALSE}
create_content(target = "my-examples", content = "shiny")
```

### Copy all examples

Copy all available examples at once:

```{r, eval = FALSE}
create_content(content = "all")
```

This will create a separate subfolder for each example in your target directory.

### Force overwrite

By default, `create_content()` skips folders that already exist. Use `force = TRUE` to overwrite:

```{r, eval = FALSE}
create_content(content = "shiny", force = TRUE)
```


