---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/sol-eng/accesstocare/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sol-eng/accesstocare/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/sol-eng/accesstocare/graph/badge.svg)](https://app.codecov.io/gh/sol-eng/accesstocare)
<!-- badges: end -->

  - [Access to Care](#access-to-care)
  - [Analysis Background](#analysis-background)
  - [Installation](#installation)
  - [Usage](#usage)
    - [Run an example](#run-an-example)
    - [Copy example](#copy-example)
    - [Copy all examples](#copy-all-examples)

## Access to Care

An R package to make it easy to view, copy, interact and publish the data 
products resulting from the Access to Care analysis.  It also contains handy
utility functions, and the data needed to create a consistent set of examples 
across the multiple data product types.

## Analysis Background 

This project combines US Census population data with hospital data provided by 
Medicare. The Census data is as of 2024, and the hospital Medicare date is as of
2025. The analysis uses individual counties as the unit of measurement. A county
is considered undeserved based on a linear model.  

## Installation

Install `accesstocare` from GitHub using: 

```{r, eval = FALSE}
pak::pak("sol-eng/accesstocare")
```

## Usage

```{r}
library(accesstocare)
```

To view the available examples, use `atc_packate_content()`. It returns a `list` object with all of the available content.  It is presented in the console, or RMarkdown, as a table. 

```{r}
atc_package_content()
```

There are three ways to use the examples:

- Open an example in your RStudio session - `atc_open_content()`
- Copy a single example to disk - `atc_copy_content()`
- Copy all examples to disk - `atc_copy_all_content()`

### Run an example

```{r, eval = FALSE}
atc_open_content()
```

```{r, echo = FALSE}
atc_package_content()
cat("18   Cancel  ")
cat("Enter the content number: ")
```

Enter the number to the left of the example in order to run it. For example, to open the `flexdashboard` example, type 3 and press enter. 

To run an example without the prompt, pass the `content_no` argument with the number.  Again, to open the `flexdashboard` use: 

```{r, eval = FALSE}
atc_open_content(3)
```

### Copy example

An example can be copied to your working directory by using `atc_copy_content()`.  It will create a new sub-folder and load the files for that particular example.

It has the same interactive mechanism as the open example function.  

```{r, eval = FALSE}
atc_copy_content()
```

```{r, echo = FALSE}
atc_package_content()
cat("18   Cancel  ")
cat("Enter the content number: ")
```

### Copy all examples

`atc_copy_all_content()` will copy all of the examples.  It will as many sub-folders as there are examples available.


