---
title: "RStudio Connect Git Manifests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RStudio Connect Git Manifests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  #eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```


## Background

Most of the examples in the `accesstocare` package can be deployed to RStudio Connect by using the RStudio IDE's button push deployment.  All of the examples are designed to be deployed using RStudio Connect's [Git Backed Deployment](https://docs.rstudio.com/connect/user/git-backed/).  This means that we tell RStudio Connect where the code repository exists, and then have RStudio Connect download the latest code everytime the repository is updated.

A major step to accomplish this, is to have a "manifest" file.  It contains the metadata of the example, such as package versions, R version, primary file, etc.  It is produced using the `rsconnect` package.  In `accesstocare`, there are two utility functions to make it easier to create the manifest files.


## Functions

There are two functions included in `accesstocare` to help with creating the manifests: 

- `atc_write_manifest()` creates the manifest for a single example
- `atc_write_all_manifests()` batch creates all of the manifests 

## Usage

We will the `fs` package to make it easy to see the changes in the directories.

```{r setup}
library(accesstocare)
library(fs)
```

For the usage examples, we will copy all of the `accesstocare` examples into a temporary folder. 

```{r}
temp_folder <- path(tempdir(), "temp")

atc_copy_all_content(temp_folder, silent = TRUE)
```


### Single example

To show how to create the manifest of a single example, we will point to the "flexdashboard" sub-folder. The `atc_copy_all_content()` command created that sub-folder. 

```{r}
dashboard_path <- path(temp_folder, "flexdashboard")

dir_tree(dashboard_path)
```

The folder contains the example, a `metadata.yml`, and a `.gitignore` file.

Now, we run create the manifest using `atc_write_manifest()`.  The function will automatically identify the primary document, and process the files listed in`.gitignore` file.  

```{r}
atc_write_manifest(dashboard_path)
```

The `manifest.json` file is now available in the sub-folder.

```{r}
dir_tree(dashboard_path)
```

### Batch create all manifests

To create the manifests for all of the sub-folders, use `atc_write_all_manifests()`.  This function will silently run the manifest writer for each sub-folder.  For those that it fails for, it skips the creation.  The function returns a `list` object with all of the results.  Printing the object on the R Console shows which were skipped, and which were created. 

```{r, include = FALSE}
t <- atc_write_all_manifests(temp_folder)
```

```{r, eval = FALSE}
atc_write_all_manifests(temp_folder)
```

```{r, echo = FALSE}
t
```


```{r}
dir_tree(temp_folder)
```

```{r, include = FALSE}
unlink(temp_folder, recursive = TRUE, force = TRUE)
```

