---
title: "RStudio Connect Git Manifests"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RStudio Connect Git Manifests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```


## Background

Most of the examples in the `accesstocare` package can be deployed to RStudio Connect by using the RStudio IDE's button push deployment.  All of the examples are designed to be deployed using RStudio Connect's [Git Backed Deployment](https://docs.rstudio.com/connect/user/git-backed/).  This means that we tell RStudio Connect where the code repository exists, and then have RStudio Connect download the latest code everytime the repository is updated.

A major step to accomplish this, is to have a "manifest" file.  It contains the metadata of the example, such as package versions, R version, primary file, etc.  It is produced using the `rsconnect` package.  In `accesstocare`, the `prepare_git_backed()` function intelligently creates manifest files.

## Function

The `prepare_git_backed()` function automatically determines whether to create a manifest for a single folder or multiple subfolders:

- If the folder contains a primary document (like an .Rmd, .qmd, app.R, etc.), it creates a manifest for that folder
- If the folder doesn't have a primary document, it checks subfolders one level deep and creates manifests for each subfolder that has a primary document 

## Usage

We will the `fs` package to make it easy to see the changes in the directories.

```{r setup}
library(accesstocare)
library(fs)
```

For the usage examples, we will copy all of the `accesstocare` examples into a temporary folder.

```{r}
temp_folder <- path(tempdir(), "temp")

create_content(target = temp_folder, content = "all", silent = TRUE)
```


### Single example

To show how to create the manifest of a single example, we will point to the "quarto-dashboard-r" sub-folder. The `create_content()` command created that sub-folder. 

```{r}
dashboard_path <- path(temp_folder, "quarto-dashboard-r")

dir_tree(dashboard_path)
```

```
/var/folders/l8/v1ym1mc10_b0dftql5wrrm8w0000gn/T/RtmpBkacCE/temp/quarto-dashboard-r
├── access-to-care.qmd
├── .gitignore
└── metadata.yml
```

The folder contains the example, a `metadata.yml`, and a `.gitignore` file.

Now, we run create the manifest using `prepare_git_backed()`.  The function will automatically identify the primary document, and process the files listed in`.gitignore` file.  

```{r}
prepare_git_backed(dashboard_path)
```

```
Full path:  /var/folders/l8/v1ym1mc10_b0dftql5wrrm8w0000gn/T/RtmpBkacCE/temp/quarto-dashboard-r
Application files
---  access-to-care.qmd
---  metadata.yml
Primary file: access-to-care.qmd
Compiling manifest...
Manifest complete

/var/folders/l8/v1ym1mc10_b0dftql5wrrm8w0000gn/T/RtmpBkacCE/temp/quarto-dashboard-r/manifest.json
```

The `manifest.json` file is now available in the sub-folder.

```{r}
dir_tree(dashboard_path)
```

```
/var/folders/l8/v1ym1mc10_b0dftql5wrrm8w0000gn/T/RtmpBkacCE/temp/quarto-dashboard-r
├── access-to-care.qmd
├── .gitignore
├── manifest.json
└── metadata.yml
```

### Batch create manifests for all subfolders

To create manifests for all subfolders at once, point `prepare_git_backed()` to the parent directory. Since the parent folder (`temp_folder`) doesn't have a primary document, the function will automatically detect subfolders with primary documents and create manifests for each. In interactive sessions, it will prompt for confirmation first. 

```{r, include = FALSE}
t <- prepare_git_backed(temp_folder)
```

```{r, eval = FALSE}
prepare_git_backed(temp_folder)
```

```{r, echo = FALSE}
t
```
```
# A tibble: 16 × 2
   content              created
   <chr>                <chr>  
 1 RMarkdown-DataPrep   YES    
 2 RMarkdown-html       YES    
 3 RMarkdown-pdf        YES    
 4 RNotebook            YES    
 5 connectwidgets       YES    
 6 dash                 YES    
 7 flexdashboard        YES    
 8 htmlwidgets          SKIPPED
 9 jupyter              YES    
10 launcher-programatic YES    
11 plot                 SKIPPED
12 plumber-api          YES    
13 powerpoint           YES    
14 powerpoint-state     YES    
15 presentation         YES    
16 shiny                YES   
```

