---
title: "Interactive plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interactive plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 4
)
```

The `accesstocare` has 3 functions that return `ggplot`/`ggiraph` plots.  They are primarily meant to keep all of the examples consistent and easier to change.  They can also be used in an interactive R session, or in your own data product.  

The included plots are:

- `atc_plot_hospitals()` returns a scatter plot comparing Hospital vs Population counts in a given county.
- `atc_plot_us_map()` returns a "hexagon" map of the USA, which includes Hawaii, Alaska, and DC. It overlays data from the Access To Care analysis.
- `atc_plot_state_map()` returns a plot with actual shape of the state, and highlights each county with a color. The color will depend on which variable is being used to plot.


```{r setup}
library(accesstocare)
```

## US Map

### Usage and options

```{r}
atc_plot_us_map()
```

```{r}
atc_plot_us_map("below")
```

```{r}
atc_plot_us_map("hospitals", 
                colors = list(high = "orange", low = "blue")
                )
```

### Interactive

```{r, eval = FALSE}
ggiraph::girafe(ggobj = atc_plot_us_map())
```

## County level plot

### Usage and options

```{r}
atc_plot_state_map()
```

```{r}
atc_plot_state_map("New York")
```

```{r}
atc_plot_state_map("New York", 
                   model_colors = list(above = "blue", below = "orange", ok = "white")
                   )
```

```{r}
atc_plot_state_map("New York", 
                   variable = "population"
                   )
```

```{r}
atc_plot_state_map("New York", 
                   variable = "population",
                   colors = list(low = "orange", high = "blue")
                   )
```

```{r}
atc_plot_state_map("New York", top_cities = 6)
```

```{r}
atc_plot_state_map("All US", top_cities = 0)
```

### Interactive

```{r, eval = FALSE}
ggiraph::girafe(ggobj = atc_plot_state_map())
```

## Hospital vs Population plot

### Usage and options

```{r}
atc_plot_hospitals()
```

```{r}
atc_plot_hospitals(show_model_results = TRUE)
```

```{r}
atc_plot_hospitals(show_model_results = TRUE,
                   model_colors = list(above = "green", below = "orange")
                   )
```

### Interactive

```{r, eval = FALSE}
ggiraph::girafe(ggobj = atc_plot_hospitals())
```
