---
title: "Access to Care Data Preparation"
output: html_document
---

## Hospital and Census data


```{r setup, include = FALSE}
library(tidyverse)
library(readxl)
```

```{r}
set.seed(100)
options(scipen=999)

library(tidyverse)
library(readxl)
```

Data provider: CMS
Data website: https://data.cms.gov/
Data URL: https://data.cms.gov/provider-data/dataset/xubh-q36u

It pulls the data from the package instead of the site.  By default, the
following code chunk does not run, unless an update is needed.

```{r, eval = FALSE}
cms <- read_csv(
  file = here::here("Hospital_General_Information.csv"), 
  name_repair = "universal"
  )

colnames(cms) <- str_to_snake(names(cms))

new_cms <- cms |> 
  rename(
    phone_number = telephone_number,
    city = city_town,
    county_name = county_parish 
    ) |> 
  select(colnames(accesstocare::cms_raw_data)) |> 
  mutate(
    county_name = case_when(
      city == "CORDOVA" & state == "AK" ~ "CHUGACH",
      city == "VALDEZ" & state == "AK" ~ "CHUGACH",
      county_name == "THE DISTRICT" ~ "DISTRICT OF COLUMBIA",
      county_name == "E. BATON ROUGE" ~ "EAST BATON ROUGE",
      county_name == "JEFFRSON DAVIS" ~ "JEFFERSON DAVIS",
      county_name == "ST. JOHN BAPTIST" ~ "ST. JOHN THE BAPTIST ",
      county_name == "LAKE OF  WOODS" & state == "MN" ~ "LAKE OF THE WOODS",
      county_name == "YELLOW MEDCINE" ~ "YELLOW MEDICINE",
      county_name == "SCOTT BLUFF" ~ "SCOTTS BLUFF",
      county_name == "DONA ANA" ~ "DOÑA ANA",
      county_name == "MAYAGUEZ" ~ "MAYAGÜEZ",
      county_name == "SAN GERMAN" ~ "SAN GERMÁN",
      county_name == "BAYAMON" ~ "BAYAMÓN",
      county_name == "MANATI" ~ "MANATÍ", 
      county_name == "NORTHWEST ARTIC BOROUGH" ~ "NORTHWEST ARCTIC BOROUGH",
      .default = county_name
    )
  ) |> 
  filter(state != "VI", state != "AS", state != "GU", state != "MP") |> 
  filter(hospital_type != "Psychiatric")
  

# Updates to CT county names

#https://libguides.ctstatelibrary.org/regionalplanning/maps
new_ct <- "Capitol | Andover, Avon, Berlin, Bloomfield, Bolton, Canton, Columbia,
Coventry, East Granby, East Hartford, East Windsor, Ellington, Enfield, Farmington, 
Glastonbury, Granby, Hartford, Hebron, Manchester, Mansfield, Marlborough, New Britain, 
Newington, Plainville, Rocky Hill, Simsbury, Somers, South Windsor, Southington, Stafford, 
Suffield, Tolland, Vernon, West Hartford, Wethersfield, Willington, Windsor, Windsor Locks
| Greater Bridgeport |	Bridgeport, Easton, Fairfield, Monroe, Stratford, Trumbull
| Lower CT River| Valley	Chester, Clinton, Cromwell, Deep River, Durham, East Haddam, 
East Hampton, Essex, Haddam, Killingworth, Lyme, Middlefield, Middletown, Old Lyme, 
Old Saybrook, Portland, Westbrook 
| Naugatuck Valley |	Ansonia, Beacon Falls, Bethlehem, Bristol, Cheshire, Derby, 
Middlebury, Naugatuck, Oxford, Plymouth, Prospect, Seymour, Shelton, Southbury, 
Thomaston, Waterbury, Watertown, Wolcott, Woodbury
| Northeast CT |	Ashford, Brooklyn, Canterbury, Chaplin, Eastford, Hampton, 
Killingly, Plainfield, Pomfret, Putnam, Scotland, Sterling, Thompson, Union, 
Voluntown, Woodstock 
| Northwest Hills	| Barkhamsted, Burlington, Canaan, Colebrook, Cornwall, Goshen, 
Hartland, Harwinton, Kent, Litchfield, Morris, New Hartford, Norfolk, North Canaan, 
Roxbury, Salisbury, Sharon, Torrington, Warren, Washington, Winchester
| South Central |	Bethany, Branford, East Haven, Guilford, Hamden, Madison, 
Meriden, Milford, New Haven, North Branford, North Haven, Orange, Wallingford, 
West Haven, Woodbridge
| Southeastern CT	| Bozrah, Colchester, East Lyme, Franklin, Griswold, Groton, 
Lebanon, Ledyard, Lisbon, Montville, New London, North Stonington, Norwich, 
Preston, Salem, Sprague, Stonington, Waterford, Windham
| Western CT	|Bethel, Bridgewater, Brookfield, Danbury, Darien, Greenwich, 
New Canaan, New Fairfield, New Milford, Newtown, Norwalk, Redding, Ridgefield, 
Sherman, Stamford, Weston, Westport, Wilton"

ct_lines <- new_ct |> 
  str_split("\\|") |> 
  unlist() |> 
  str_trim() |> 
  str_remove_all("\\t")
sel <-c(1,3,5,7,9,11,13,15,17)

ct_counties <- ct_lines[sel] |> 
  str_replace("CT", "Connecticut") 

ct_counties[ct_counties == "Lower Connecticut River"] <- "Lower Connecticut River Valley" 
ct_counties[ct_counties == "Northeast Connecticut"] <- "Northeastern Connecticut"  
ct_counties[ct_counties == "South Central"] <- "South Central Connecticut"

ct_towns <- ct_lines[sel + 1] |> 
  str_split(",") |> 
  set_names(ct_counties)

new_ct <- ct_towns |> 
  imap(\(x, y) tibble(county = y, city_name = x)) |> 
  bind_rows() |> 
  mutate(city_name = str_trim(city_name)) |> 
  mutate(
    city = str_to_upper(city_name),
    ct_county = str_to_upper(county)
    ) |> 
  select(city, ct_county) |> 
  mutate(state = "CT")

cms_raw_data <- new_cms |> 
  mutate(city = case_when(
    city == "WILLIMANTIC" & state == "CT" ~  "WINDHAM",
    city == "STAFFORD SPRINGS" & state == "CT" ~  "STAFFORD",
    city == "MANSFIELD CENTER" & state == "CT" ~ "MANSFIELD",
    .default = city
  )) |> 
  left_join(new_ct, by = c("state", "city")) |> 
  mutate(county_name = ifelse(!is.na(ct_county), ct_county, county_name)) |> 
  select(-ct_county)

usethis::use_data(cms_raw_data, overwrite = TRUE)
```

Quick function to create a consistent match key for the county names

```{r}
create_match_key <- function(x) {
  x |> 
    mutate(match_key = county_name) |> 
    mutate(match_key = str_to_upper(match_key)) |> 
    mutate(match_key = str_remove(match_key, "BOROUGH")) |> 
    mutate(match_key = str_remove(match_key, "CENSUS AREA")) |> 
    mutate(match_key = str_remove(match_key, "MUNICIPALITY")) |> 
    mutate(match_key = str_remove(match_key, "PARISH")) |> 
    mutate(match_key = str_remove(match_key, "COUNTY")) |> 
    mutate(match_key = str_remove(match_key, "MUNICIPIO")) |> 
    mutate(match_key = str_remove(match_key, "PLANNING REGION")) |> 
    mutate(match_key = str_remove(match_key, "BOROUH")) |> 
    mutate(match_key = str_remove(match_key, "CITY AND")) |> 
    mutate(match_key = str_remove_all(match_key, "'")) |> 
    mutate(match_key = str_remove_all(match_key, " ")) |> 
    mutate(match_key = str_remove_all(match_key, "\\.")) |> 
    mutate(match_key = str_trim(match_key)) |> 
    mutate(match_key = paste0(state, "-", match_key)) 
}
```


Uses the `usmap` data to retrieve the FIPS code for each county.  Performs close 
to the same transformations to the county names to produce the matches

```{r}
county_fips<- usmap::countypop |> 
  select(
    fips,
    state = abbr,
    county_name = county
  ) |> 
  mutate(
    county_name = case_when(
      fips == 35013 ~ "	DOÑA ANA",
      .default = county_name
    )
  ) |> 
  create_match_key() |> 
  select(fips, match_key)

county_fips
```

Creates state and state abbreviation table

```{r}
states_tbl <- tibble(
  state = c(state.abb, "PR", "DC"),
  state_name = c(state.name, "Puerto Rico", "District of Columbia")
)
states_tbl
```


Confirms that there are no un-matched counties

```{r}
cms_raw_data |> 
  summarize(.by = c(state, county_name)) |> 
  create_match_key() |> 
  left_join(county_fips, by = "match_key") |> 
  filter(is.na(fips))
```

Prepares the `us_hospitals` data set.

```{r}
us_hospitals <- cms_raw_data |> 
  create_match_key() |> 
  left_join(county_fips, by = "match_key") |> 
  left_join(states_tbl, by = "state") |> 
  select(
    facility_id, facility_name, address, city, 
    zip_code, fips, state, county_name, state_name
    ) |> 
  arrange(state, county_name)
```

Census data for year 2024

```{r}
census_us <- read_xlsx(here::here("co-est2024-pop.xlsx"), range = "A5:G3149") |> 
  select(c(1,7)) |> 
  rename(county = `United States`, population = `340110988`) |> 
  separate_wider_delim(county, ",", names = c("county", "state_name")) |> 
  mutate(
    state_name = str_trim(state_name), 
    county = str_remove_all(county, "\\.")
    )

census_pr <- read_xlsx(here::here("prm-est2024-pop.xlsx"), range = "A5:G83") |> 
  select(c(1,7)) |> 
  rename(county = `Puerto Rico`, population = `3203295`) |> 
  separate_wider_delim(county, ",", names = c("county", "state_name")) |> 
  mutate(
    state_name = str_trim(state_name), 
    county = str_remove_all(county, "\\.")
  )

county_tbl <- census_us |> 
  bind_rows(census_pr) |> 
  left_join(select(us_states, state_name, state), by = "state_name") |> 
  mutate(state = ifelse(state_name == "Puerto Rico", "PR", state)) |> 
  rename(county_name = county) |> 
  arrange(state, county_name) |> 
  create_match_key() |> 
  left_join(county_fips, by = "match_key") |> 
  select(-match_key) |> 
  select(fips, state, state_name, county_name, population) 

county_tbl
```



Prepares data for the model, and produces the `us_model` variable.

```{r}
cnt_hosp <- us_hospitals |> 
  count(fips, name = "hospitals") |> 
  right_join(county_tbl, by = "fips")

cnt_hosp2 <- cnt_hosp |> 
  replace_na(list(hospitals = 0)) |> 
  select(fips, state, county_name, hospitals, population) |> 
  arrange(state, county_name)

us_model <- cnt_hosp2 |> 
  sample_frac(0.3) |> 
  lm(hospitals ~ population, data = _) 

preds <- predict(
  us_model, 
  newdata = cnt_hosp2, 
  interval = "prediction",
  level = 0.99
  ) |> 
  as_tibble() |> 
  rename_all(function(x) paste0("pred_", x))
```

Matches the county data with the predictions to create the `us_counties` data set

```{r}
us_counties <- cnt_hosp2 |> 
  bind_cols(preds) |> 
  mutate(
    pred_lwr = round(pred_lwr),
    pred_fit = round(pred_fit),
    pred_upr = round(pred_upr),
    pred_lwr = ifelse(pred_lwr < 0, 0, pred_lwr),
    pred_fit = ifelse(pred_fit < 0, 0, pred_fit),
    pred_upr = ifelse(pred_upr < 0, 0, pred_upr),
    pred_status = case_when(
      hospitals < pred_lwr ~ "below",
      hospitals > pred_upr ~ "above",
      TRUE ~ "ok"
    )
  ) |> 
  left_join(states_tbl, by = "state")

```

```{r}
us_states <- us_counties |> 
  group_by(state) |> 
  summarise(
    hospitals = sum(hospitals),
    population = sum(population)
  ) |> 
  ungroup() |> 
  mutate(
    per_person = round(population / hospitals),
    per_person_quartile = ntile(per_person, 4)
  ) |> 
  left_join(states_tbl, by = "state")
```

## Hex map

```{r}
library(hexbin)

sh <- hexcoords(0.5, 0.5)

st_locations_list <- list(
  list(state = "MS", x = 0, y = 0),
  list(state = "AL", x = 1, y = 0),
  list(state = "GA", x = 2, y = 0),
  list(state = "FL", x = 1.5, y = -1.5),
  list(state = "LA", x = -1, y = 0),
  list(state = "OK", x = -2, y = 0),
  list(state = "TX", x = -1.5, y = -1.5),
  list(state = "AZ", x = -3, y = 0),
  list(state = "TN", x = 0.5, y = 1.5),
  list(state = "AR", x = -0.5, y = 1.5),
  list(state = "KS", x = -1.5, y = 1.5),
  list(state = "NM", x = -2.5, y = 1.5),
  list(state = "UT", x = -3.5, y = 1.5),
  list(state = "CA", x = -4.5, y = 1.5),
  list(state = "NC", x = 1.5, y = 1.5),
  list(state = "SC", x = 2.5, y = 1.5),
  list(state = "DC", x = 3.5, y = 1.5),
  list(state = "OR", x = -5, y = 3),
  list(state = "NV", x = -4, y = 3),
  list(state = "CO", x = -3, y = 3),
  list(state = "NE", x = -2, y = 3),
  list(state = "MO", x = -1, y = 3),
  list(state = "KY", x = 0, y = 3),
  list(state = "WV", x = 1, y = 3),
  list(state = "VA", x = 2, y = 3),
  list(state = "MD", x = 3, y = 3),
  list(state = "DE", x = 4, y = 3),
  list(state = "CT", x = 4.5, y = 4.5),
  list(state = "NJ", x = 3.5, y = 4.5),
  list(state = "PA", x = 2.5, y = 4.5),
  list(state = "OH", x = 1.5, y = 4.5),
  list(state = "IN", x = 0.5, y = 4.5),
  list(state = "IL", x = -0.5, y = 4.5),
  list(state = "IA", x = -1.5, y = 4.5),
  list(state = "SD", x = -2.5, y = 4.5),
  list(state = "WY", x = -3.5, y = 4.5),
  list(state = "ID", x = -4.5, y = 4.5),
  list(state = "WA", x = -5, y = 6),
  list(state = "MT", x = -4, y = 6),
  list(state = "ND", x = -3, y = 6),
  list(state = "MN", x = -2, y = 6),
  list(state = "WI", x = -1, y = 6),
  list(state = "MI", x = 1, y = 6),
  list(state = "NY", x = 3, y = 6),
  list(state = "MA", x = 4, y = 6),
  list(state = "RI", x = 5, y = 6),
  list(state = "NH", x = 4.5, y = 7.5),
  list(state = "VT", x = 3.5, y = 7.5),
  list(state = "ME", x = 5, y = 9),
  list(state = "AK", x = -5, y = 9),
  list(state = "HI", x = -5, y = -1.5),
  list(state = "PR", x = 4.5, y = -1.5)
)

us_hex_positions <- st_locations_list |> 
  map_dfr(~.x) |> 
  left_join(states_tbl, by = "state")

us_hex_polygons <- map_dfr(
  st_locations_list,
  ~{
    tibble(
      x = sh$x + .x$x,
      y = sh$y + .x$y,
      state = .x$state
    )
  }
)

us_hex_polygons |> 
  ggplot() +
  geom_polygon(aes(x, y, group = state), fill = "lightgray", color = "white") +
  geom_text(aes(x, y, label = state), data = us_hex_positions) +
  theme_void() +
  theme(legend.position = "none") 
```



```{r}
pred_count <- us_counties |> 
  count(state, pred_status) |> 
  pivot_wider(
    names_from = pred_status, 
    values_from = n, 
    values_fill = 0,
    names_prefix = "pred_"
    )

us_atc_state_polygons <- us_states |> 
  inner_join(us_hex_polygons, by = "state") |> 
  inner_join(pred_count, by = "state")
```

## County  polygons

```{r}
library(sf)
county_map <- usmap::us_map("county") 

coord_map <- NULL
for(i in seq_len(nrow(county_map))){
  row_map <- county_map[i, ]
  row_tbl <- row_map |> 
    st_coordinates() |> 
    as_tibble() |> 
    mutate(fips = row_map$fips)
  coord_map <- coord_map |> 
    bind_rows(row_tbl)
} 

coord_map <- coord_map |> 
  mutate(
    hole = L2 != 1,
    group = paste0(fips, ".", L2)
    ) |> 
  rename(
    x = X,
    y = Y,
    piece = L2
    ) |> 
  select(fips, x, y, hole, piece, group)


us_atc_county_polygons <- us_counties |>   
  left_join(coord_map, by = "fips") 
```

```{r, eval = FALSE}
us_large_cities <- maps::us.cities |> 
  select(long, lat, everything()) |> 
  usmap::usmap_transform() |> 
  select(-lat, -long) |> 
  rename(x = long.1, 
         y = lat.1, 
         city_name = name, 
         state = country.etc,
         population = pop
         ) |> 
  mutate(city_name = str_sub(city_name, 1, nchar(city_name) - 3)) |> 
  arrange(state, -population) |> 
  group_by(state) |> 
  mutate(position = row_number()) |> 
  ungroup()
```

```{r}
palette_atc <- list(
    above = "#0072B2",
    below =  "#CC79A7",
    ok = "#009E73",
    low = "#ffffff",
    high = "#0072B2",
    ambulance = "#E69F00"
  )

```
 
```{r}
us_atc_model <- us_model 
```

```{r, eval = FALSE}
if(Sys.getenv("R_CONFIG_ACTIVE") == "rsconnect") {
  boardname <- "rsconnect"
  board_register_rsconnect(
    server = Sys.getenv("CONNECT_SERVER"),
    key = Sys.getenv("CONNECT_API_KEY")
    )
  
  pin(
    us_counties,
    name = "atc-counties",
    board = boardname
  )
  
  pin(
    us_states,
    name = "atc-states",
    board = boardname
  )
  
  pin(
    us_hospitals,
    name = "atc-hospitals",
    board = boardname
  )
  
  pin(
    us_atc_model,
    name = "atc-model",
    board = boardname
  )
}
```


```{r, echo = FALSE, eval = FALSE}

library(usethis)

use_data(us_hex_positions, overwrite = TRUE)
use_data(us_hex_polygons, overwrite = TRUE)
use_data(us_hospitals, overwrite = TRUE)
use_data(us_counties, overwrite = TRUE)
use_data(us_states, overwrite = TRUE)

use_data(us_atc_county_polygons, overwrite = TRUE)
use_data(us_atc_state_polygons, overwrite = TRUE)

use_data(us_large_cities, overwrite = TRUE)

use_data(us_atc_model, overwrite = TRUE)

use_data(palette_atc, overwrite = TRUE)
```



